---
title: "Lab 09 - Grading the professor, Pt. 1"
author: "Alex Connolly"
date: "03/22/22"
output: github_document
---

### Load packages and data

```{r load-packages, message=FALSE}
library(tidyverse) 
library(tidymodels)
library(openintro)
```

### Exercise 1

```{r distro}
evals %>%
  ggplot(mapping = aes(x=score)) + geom_histogram()
```

This is skewed. Students rate courses generally higher. This is not that unexpected, given how most of my evals I tend to land on 4 or 5, and only the really bad professors/courses get 1-2s.



### Exercise 2


```{r scatter}
evals %>%
  ggplot(mapping = aes(x=bty_avg, y=score)) + geom_point()
```
Honestly, this doesn't look that representative. There are plenty of "ugly" professors who peoplestill rated highly, and plenty of "beautiful" professors that got medicore scores. There aren't many awful scores that got high beauty ratings though. 

### Excersise 3

```{r jitter}
evals %>%
  ggplot(mapping = aes(x=bty_avg, y=score)) + geom_jitter()
```
Jitter adds a small amount of variation to location of each point, so you can see points that otherwise were on top of each other. In the original scatterplot, it appears as if there are many points that are the exact same point on the graph, so the original graph only shows them each once. 

### Exercise 4


```{r linear}
m_bty <- lm(score ~ bty_avg, data=evals)

print(m_bty)

summary(m_bty)
```

```{r plot}
evals %>%
  ggplot(mapping = aes(x=bty_avg, y=score)) + geom_jitter()
```




## 
For Exercise 12, relevel() function can be helpful! 
